Title

### 2012-07-10 inc/external_forces/external_forces.tex
continuing to move \section directives into subimported files

A magnetic lens may be modeled using one linear force contribution.
Unfortunately, it is not practical to write an analytic form of the magnitude of this term; the field distribution is very complicated to describe\cite{montgomery_some_1961} and the ``lensing'' action is actually a compound force (first rotating the beam, then lensing).
We have found that in practice, characterizing a specific magnetic lens ($M_{\smallT}(I)$ where $I$ is the current in the magnetic lens) is much easier than attempting to find a generic functional form.

>>>>

A magnetic lens may be modeled using one linear force contribution.
Unfortunately, it is not practical to write an analytic form of the magnitude of this term; the field distribution is very complicated to describe\cite{montgomery_some_1961} and the ``lensing'' action is actually a compound force (first rotating the beam, then lensing, see Section \ref{sec:mag_lens}).
We have found that in practice, characterizing a specific magnetic lens ($M_{\smallT}(I)$ where $I$ is the current in the magnetic lens) is much easier than attempting to find a generic functional form.
